Efficient Calculation of Polynomial Features on Sparse Matrices

### 2016-02-12 paper/workshop/sparse_poly.tex
fixed indices in mapping definition
dimensionality in abstract

\usepackage{amsmath}
\usepackage{mathtools}

@@

\begin{abstract}
We provide an algorithm for polynomial feature expansion that can operate directly on sparse a
matrix of size $NxD$ with $O(d^kD^kN)$ where $k$ is the polynomial order and $d$ is the density of each row.

@@

$(i_0, i_1, \dots, i_{k-1}) \mapsto {0,1,\dots, \binom{D}{k}}$ 
$\forall i_0, i_1, \dots, i_{k-1} \mid 0 \le i_0 \le i_1 \le \dots \le i_{k-1} \le D$

where $i_0,i_1,\dots i_{k-1}$ are column indicies.

>>>>

\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{amssymb}

@@

\begin{abstract}
We provide an algorithm for polynomial feature expansion that can operate directly on sparse a
matrix of size $N \times D$ with $O(d^kD^kN)$ where $k$ is the polynomial order and $d$ is the density of each row.

@@

\begin{equation}
(x_{i_0}, x_{i_1}, \dots, x_{i_{k-1}}) \rightarrowtail \hspace{-1.9ex} \twoheadrightarrow p_{i_0i_1 \dots i_{k-1}} \in \{0,1,\dots, \binom{D}{k}\} 
\forall (i_0, i_1, \dots, i_{k-1})
\end{equation}
such that $ 0 \le i_0 \le i_1 \le \dots \le i_{k-1} < D$
where $(x_{i_0}, x_{i_1}, \dots, x_{i_{k-1}})$ are column indicies of a row vector $\vec{x}$ of an $N \times D$ input matrix and $p_{i_0i_1 \dots i_{k-1}}$ is a column index of the polynomial expansion matrix.
